\LARGE \bf Grupo Bimbo Inventory Demand Data Science Report

### 2024-07-15 src/data-science-project/data_science_project/docs/paper/paper.tex
Docs 96 percent
Conclusion Documents
Images Documents

\section{RESULTS}
The performance of the XGBoost and Random Forest models was evaluated based on the RMSE. The Random Forest model achieved an RMSE of X, indicating better predictive accuracy compared to the XGBoost model, which had an RMSE of Y. The superior performance of Random Forest can be attributed to its ability to handle high-dimensional data and its robustness to overfitting. The inclusion of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, further enhanced the model's predictive capabilities.

\begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/comparison.jpg}
        \caption{Actual vs Predict Adjusted Demand}
        \end{center}
\end{figure}

\begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/comparisonxg.jpg}
        \caption{Actual vs Predict Adjusted Demand}
        \end{center}
\end{figure}

@@

This study demonstrates the potential of machine learning models in forecasting product demand for Grupo Bimbo. The XGBoost model outperformed the Random Forest model, offering more accurate predictions of adjusted demand. The integration of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, proved beneficial in enhancing the model's accuracy. These insights can be leveraged to improve inventory management, reduce waste, and optimize resource allocation. Future work could explore the integration of additional features, such as macroeconomic indicators and weather data, to further enhance prediction accuracy. Additionally, implementing these models in a real-time production environment could provide continuous insights and adaptive inventory strategies.

>>>>

\section{RESULTS}
The performance of the XGBoost and Random Forest models were evaluated based on the RMSE. The Random Forest model achieved an RMSE of X, indicating better predictive accuracy compared to the XGBoost model, which had an RMSE of Y. The superior performance of Random Forest can be attributed to its ability to handle high-dimensional data and its robustness to overfitting. The inclusion of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, further enhanced the model's predictive capabilities.

\begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.5\textwidth]{images/comparison.jpg}
        \caption{Actual vs Predict Adjusted Demand}
        \end{center}
\end{figure}

\begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.5\textwidth]{images/comparisonxg.jpg}
        \caption{Actual vs Predict Adjusted Demand}
        \end{center}
\end{figure}

@@

This study demonstrates the potential of machine learning models in forecasting product demand for Grupo Bimbo. The Random Forest model outperformed the XGBoost model, offering more accurate predictions of adjusted demand. The integration of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, proved beneficial in enhancing the model's accuracy. These insights can be leveraged to improve inventory management, reduce waste, and optimize resource allocation. Future work could explore the integration of additional features, such as macroeconomic indicators and weather data, to further enhance prediction accuracy. Additionally, implementing these models in a real-time production environment could provide continuous insights and adaptive inventory strategies.
